---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# xutils

<!-- badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/xutils)](https://CRAN.R-project.org/package=xutils)
[![CRAN_Downloads](http://cranlogs.r-pkg.org/badges/grand-total/xutils)](https://CRAN.R-project.org/package=xutils)
[![R-CMD-check](https://github.com/fangzhou-xie/xutils/workflows/R-CMD-check/badge.svg)](https://github.com/fangzhou-xie/xutils/actions)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

This is a package that contains functions dealing with data,
which I personally found useful. Hence the name:
**x**utils.

## Installation

<!-- This package is planned to be submitted to CRAN. -->
You can install the released version of `xutils` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("xutils")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fangzhou-xie/xutils")
```

## Example

This is a basic example of using the only function in `xutils` package: the `html_decode` function.

```{r example}
# load library
library(xutils)
# create test strings
strings <- c("abcd", "&amp; &apos; &gt;", "&amp;", "&euro; &lt;")
# decode
html_decode(strings)
```

## License

The package is distributed under MIT license.
