---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r echo = FALSE, results = "hide", message = FALSE}
library(badger)
```

# xutils

<!-- badges: start -->
```{r, echo = FALSE, results = "asis"}
cat(
  badge_cran_release("xutils", "green"),
  badge_cran_download("xutils", "grand-total", "green"),
  badge_cran_checks("xutils"),
  badge_last_commit("fangzhou-xie/xutils")
)
```
[![Build Status](https://travis-ci.com/fangzhou-xie/xutils.svg?branch=main)](https://travis-ci.com/github/fangzhou-xie/xutils)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

This is a package that contains functions dealing with data,
which I personally found useful. Hence the name:
**x**utils.

## Installation

<!-- This package is planned to be submitted to CRAN. -->
You can install the released version of `xutils` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("xutils")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fangzhou-xie/xutils")
```

## Example

This is a basic example of using the only function in `xutils` package: the `html_decode` function.

```{r example}
# load library
library(xutils)
# create test strings
strings <- c("abcd", "&amp; &apos; &gt;", "&amp;", "&euro; &lt;")
# decode
html_decode(strings)
```

## License

The package is distributed under MIT license.
